Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-12-09 manuscript/ensembler.tex
Appendix converted to Figure at request of PLoS Comp Biol.

\begin{figure*}[tbp]
    \includegraphics[width=\textwidth]{nstructures_per_tk_target/nstructures_per_tk_target.pdf}
    \caption{{\bf Number of PDB structures available for each TK target.}
    \color{red}
    Data is shown for each of the 93 TK kinase domains. The labels indicate the UniProt name for the target protein plus an index for the kinase domain (three of the selected proteins have two kinase domains). Each PDB chain is counted individually, and only chains which contain the target domain are counted.
}
    \label{figure:nstructures-per-tk-target}
\end{figure*}

@@

\color{red}
{\bf Comparison with known biochemically relevant conformations.}
To evaluate the models of \emph{Src} and \emph{Abl1} in the context of the published structural biology literature on functionally relevant conformations, we have focused on two residue pair distances thought to be important order parameters for the regulation of protein kinase domain activity.
We use the residue numbering schemes for chicken Src (commonly employed in the literature even in reference to human Src)~\cite{xu:1999:2src, cowan-jacob:2005:1y57} and human Abl1 isoform A~\cite{young:2006:2f4j, cowan-jacob:2006:2hyy, levinson:2006:2g1t} respectively; the exact numbering schemes are provided in Appendix \ref{si:residue-numbering-schemes}.
\color{black}

@@

\onecolumngrid
\newpage
\appendix
\setcounter{figure}{0}

\renewcommand{\thesection}{\arabic{section}}
\section{Sequences and residue numbering schemes for Src and Abl1}
\label{si:residue-numbering-schemes}

Kinase catalytic domains are highlighted in red, and the conserved residues analyzed in the main text (Figs.~\ref{figure:src-ref-structures} and~\ref{figure:pair-distances}) are highlighted with yellow background.

\subsubsection*{Human Abl1 sequence}

@@

\subsubsection*{Sequences for human and chicken Src, aligned using Clustal Omega}

@@

% \section{Figures}

>>>>

\begin{figure*}[tbp]
    \includegraphics[width=\textwidth]{nstructures_per_tk_target/nstructures_per_tk_target.pdf}
    \caption{{\bf Number of PDB structures available for each TK target.}
    \color{red}
    Data is shown for each of the 93 TK kinase domains, sorted in order of the number of available PDB structures for each domain. 
    The labels indicate the UniProt name for the target protein plus an index for the kinase domain (three of the selected proteins have two kinase domains). 
    Each PDB chain is counted individually, and only chains which contain the target domain are counted.
}
    \label{figure:nstructures-per-tk-target}
\end{figure*}

@@

\color{red}
{\bf Comparison with known biochemically relevant conformations.}
To evaluate the models of \emph{Src} and \emph{Abl1} in the context of the published structural biology literature on functionally relevant conformations, we have focused on two residue pair distances thought to be important order parameters for the regulation of protein kinase domain activity.
We use the residue numbering schemes for chicken Src (commonly employed in the literature even in reference to human Src)~\cite{xu:1999:2src, cowan-jacob:2005:1y57} and human Abl1 isoform A~\cite{young:2006:2f4j, cowan-jacob:2006:2hyy, levinson:2006:2g1t} respectively; the exact numbering schemes are provided in Fig.~\ref{figure:residue-numbering-schemes}.
\color{black}

@@

\onecolumngrid
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE: Sequences and residue numbering schemes for Src and Abl1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[tb]

\begin{centering}
\emph{Human Abl1 sequence}

\end{centering}

@@

\begin{centering}
\emph{Sequences for human and chicken Src, aligned using Clustal Omega}

\end{centering}

@@

    \caption{{\bf Sequences and residue numbering schemes for Src and Abl1.}
Kinase catalytic domains are highlighted in red, and the conserved residues analyzed in the main text (Figs.~\ref{figure:src-ref-structures} and~\ref{figure:pair-distances}) are highlighted with yellow background.
  }
  \label{figure:residue-numbering-schemes}
\end{figure}
